A Stochastic Quasi-Newton Optimizer for TensorFlow

### 2018-05-06 paper/main.tex
Section 3 draft.

\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{optidef}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}

@@

>>>>

\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{optidef}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{listings}

\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}

\lstdefinestyle{mystyle}{
  commentstyle=\color{codegreen},
  keywordstyle=\color{magenta},
  numberstyle=\tiny\color{codegray},
  stringstyle=\color{codepurple},
  basicstyle=\footnotesize\tt,
  breakatwhitespace=false,         
  breaklines=true,                 
  captionpos=b,                    
  keepspaces=true,                 
  numbers=left,                    
  numbersep=5pt,                  
  showspaces=false,                
  showstringspaces=false,
  showtabs=false,                  
  tabsize=2
}

\lstset{style=mystyle}

@@

Our optimization object, \texttt{SQNOptimizer}, is implemented using
\texttt{NumPy} \cite{numpy} with \texttt{ndarray} objects serving as the primary
data structures for the numerical computations in Algorithm \ref{alg:sdlbfgs}.
It inherits the features of the \texttt{ExternalOptimizerInterface}, which
packages the objective function and its gradients from the network model in use
and presents it in a \texttt{NumPy}-interoperable format.

The general framework for using built-in \texttt{Optimizer} objects follows the
structure presented in Figure \ref{fig:typical}.
\begin{figure}[h]
  \begin{lstlisting}[language=Python]
# ... setup
optimizer = Optimizer(**kwargs).minimize(objective_function)
# ... setup
with tf.Session() as session:
    # ... training setup
    optimizer.run(**training_kwargs)
  \end{lstlisting}
  \caption{The typical workflow for using built-in \texttt{Optimizer} objects in
    a statistical learning setting. Here the \texttt{optimizer} is an operation
    which is configured to minimize the objective function. The actual
  minimization occurs inside of the session block.}
  \label{fig:typical}
\end{figure}
The initialization of line 2 indicates that \texttt{optimizer} is a minimization
operation, rather than the result of a minimization. By contrast, for subclasses
of an \texttt{ExternalOptimizerInterface}, this structure is replaced by the
workflow in Figure \ref{fig:external}.
\begin{figure}[h]
  \begin{lstlisting}[language=Python]
# ... setup
optimizer = ExternalOptimizer(objective_function, **kwargs)
# ... setup
with tf.Session() as session:
    # ... training setup
    optimizer.minimize(session, **training_kwargs)
  \end{lstlisting}
  \caption{%
    The workflow for using objects of 
  \texttt{ExternalOptimizerInterface} subclasses, such as the implementation of
  \texttt{SQNOptimizer}. Here the \texttt{optimizer} itself is the minimizer while
  the \texttt{minimize} method actually performs estimation of the minimal
  objective function value.  }
  \label{fig:external}
\end{figure}

Now, the \texttt{minimize} method returns the \emph{result} of a minimization
rather than a minimization operation. As \texttt{SQNOptimizer} inherits this
functionality, the second workflow is required.
